 %-------------------------
% Resume in Latex
% Author : Martin Klein
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{wrapfig}
\usepackage[document]{ragged2e}
\usepackage{multicol}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ - #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.martinklein.co/}{\Large Martin Klein}}  & \href{mailto:martin.t.klein@gmail.com}{martin.t.klein@gmail.com}\\
   \textit{PhD in Energy Systems Analysis} & \href{https://www.martinklein.co/}{https://www.martinklein.co/}   \\

\end{tabular*}

\bigskip 


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {50Hertz Transmission GmbH}{Berlin, Germany}
      {Associate, Department Strategic Grid Planning}{Apr 2021 -- Present}
      \resumeItemListStart
        \resumeItem{Strategic Planning and Energy Scenario Development}
          {Spearheaded the formulation of long-term energy scenarios, considering key uncertainties and decarbonization strategies for the energy system. Prepared regionalization data for grid models.

          \textit{Key Contribution}: Enabled robust strategic planning by providing critical scenario inputs for Germany's 2045 grid development plan, aimed at achieving net-zero emissions.}
      \resumeItemListEnd

        \medskip


    \resumeSubheading
      {IU International University of Applied Sciences}{Remote}
      {Lecturer for Electrical Engineering}{Apr 2022 - Mar 2023}
      \resumeItemListStart
        \resumeItem{Course Development and Instruction}
          {Developed and delivered an introductory Python programming course, facilitating learning for students of varying proficiency levels.

          \textit{Key Contribution}: Cultivated an engaging learning environment, enhancing student engagement and comprehension.}
      \resumeItemListEnd

        \medskip


    \resumeSubheading
      {Volue Insight}{Berlin, Germany}
      {Market Analyst}{Apr 2020 -- Mar 2021}
      \resumeItemListStart
        \resumeItem{Power System Modeling and Market Analysis}
          {Managed a unit-commitment electricity market model for 19 European countries, responsible for forecasting market prices and power balances.

          \textit{Key Contribution}: Enhanced regional market intelligence by reliably forecasting power market dynamics for Central Western Europe, Iberia, UK, Central, and Southern Eastern Europe.}

        \resumeItem{Data Pipeline Management}
          {Oversaw and automated cloud-based data flows and analysis routines.

          \textit{Key Contribution}: Ensured daily delivery of electricity market forecasts in a data-as-a-service context, increasing operational efficiency and data reliability.}
        \medskip
      \resumeItemListEnd

      \medskip
      %Remaining CV sections to follow the above format
      \resumeSubHeadingListEnd
\bigskip



\bigskip 

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {University of Stuttgart}{Stuttgart, Germany}
      {Doctor of Philosophy in Energy Engineering}{Oct 2015 -- Jun 2020}
      \resumeItemListStart
        \resumeItem{Thesis}
          {Title: "Agent-Based Modeling and Simulation of Renewable Energy Market Integration -- The Case of PV-Battery Systems"
          Examiners: Prof. Andre Thess, Prof. Laurens de Vries}
      \resumeItemListEnd

    \resumeSubheading
      {Helmholtz Association}{Stuttgart and Karlsruhe, Germany}
      {Helmholtz Research School on Energy Scenarios}{May 2015 -- Sep 2017}

    \resumeSubheading
      {Delft University of Technology}{Delft, The Netherlands}
      {Visiting Researcher, Faculty of Technology, Policy and Management}{Oct 2016 -- Dec 2016}

    \resumeSubheading
      {University of Freiburg}{Freiburg, Germany}
      {Master of Science in Renewable Energy Management}{Oct 2011 -- Dec 2013}
      \resumeItemListStart
        \resumeItem{Academic Performance}
          {Finished with a top score of 1.0 (equivalent to GPA: 4.0)}
      \resumeItemListEnd

    \resumeSubheading
      {KTH Royal Institute of Technology}{Stockholm, Sweden}
      {Exchange Semester, Physics Department}{Jan 2011 -- Jun 2011}

    \resumeSubheading
      {RWTH Aachen University}{Aachen, Germany}
      {Bachelor of Science in Physics}{Oct 2007 -- Sep 2010}
      \resumeItemListStart
        \resumeItem{Academic Performance}
          {Graduated with a high score of 1.3 (equivalent to GPA: 3.7)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\bigskip


%-------- SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem
      {Programming & Tools}{Proficient in Python (8+ years, including extensive experience with pandas, numpy, scikit-learn, and FastAPI), Plexos, PyPSA, Git/Github, Java, SQL}
    \resumeSubItem
      {Analytical Methods}{Expertise in agent-based modeling, optimization (LP, genetic algorithm, gradient methods), machine learning, scenarios, and Monte Carlo simulation}
    \resumeSubItem
      {Languages}{German (Native), English (Business Fluent), French (Basic)}
  \resumeSubHeadingListEnd
\bigskip


\bigskip 

%-------- AWARDS------------
\section{Awards}
  \resumeSubHeadingListStart
    \resumeSubItem
     {Summa cum laude}{PhD thesis (2020)}
    \resumeSubItem
     {Best in class}{M.Sc. Renewable Energy Management (2013)}
    \resumeSubItem
     {With distinction}{B.Sc. Physics (2010)}
         \resumeSubItem
     {Scholarship}{German Academic Scholarship Foundation (German: ``Studienstiftung'') (2008-2013)}
         \resumeSubItem
     {Best in class}{A level (German: ``Abitur'') (2007)}
  \resumeSubHeadingListEnd


\bigskip 
\bigskip




%-------- PUBLICATIONS ------------
\section{Publications (selection)}
  \resumeSubHeadingListStart
    \resumeSubItem
      {Xiao, M., Junne, T., Haas, J., Klein, M., 2021.}
      {``Plummeting costs of renewables - Are energy scenarios lagging?'' \textit{Energy Strategy Reviews}, 35. Explored the economic feasibility of renewable energy, influencing energy policy making. DOI: 10.1016/j.esr.2021.100636.}

    \resumeSubItem
      {Klein, M., Frey, U., Reeg, M., 2019}
      {``Models Within Models -- Agent-Based Modelling and Simulation in Energy Systems Analysis.'' \textit{Journal of Artificial Societies and Social Simulation}, 4. Introduced innovative modeling approaches to optimize energy systems. DOI: 10.18564/jasss.4129.}

    \resumeSubItem
      {Klein, M., Ziade, A., de Vries, L., 2019}
      {``Aligning prosumers with the electricity wholesale market - The impact of time-varying price signals and fixed network charges on solar self-consumption.'' \textit{Energy Policy}, 134. Provided strategic insights on improving solar energy consumption. DOI: 10.1016/j.enpol.2019.110901.}

    \resumeSubItem
      {Frey, U., Klein, M., Deissenroth, M., 2019. }
      {``Modelling complex investment decisions in Germany for Renewables with different machine learning algorithms.'' \textit{Environmental Modelling and Software}, 118. Advanced renewable energy investment decision-making using machine learning. DOI: 10.1016/j.envsoft.2019.03.006.}

    \resumeSubItem
      {Klein, M., Deissenroth, M., 2017.}
      {``When do households invest in solar photovoltaics? An application of prospect theory.'' \textit{Energy Policy}, 109. Explored the consumer behavior towards solar photovoltaics investment. DOI: 10.1016/j.enpol.2017.06.067.}
  \resumeSubHeadingListEnd
\bigskip



\bigskip 
\end{document}
